%% Copyright 2006-2010 Xavier Danaux (xdanaux@gmail.com).
%% Copyright 2010-2011 Mark Liu (markwayneliu@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.

\documentclass[10pt,a4paper,sans]{moderncv}

\usepackage{verbatim}

\moderncvstyle{classic}
\moderncvcolor{blue}

\usepackage[utf8]{inputenc}

\usepackage[top=1in,bottom=1in,scale=0.8]{geometry}
\usepackage{multicol}
\renewcommand*{\namefont}{\fontsize{30}{40}\mdseries\upshape}

\usepackage{etoolbox}
\patchcmd{\makecvtitle}{{minipage}[b]}{{minipage}[t]}{}{}
\patchcmd{\makecvtitle}{{tabular}[b]}{{tabular}}{}{}

\firstname{Tyler}
\familyname{Hou}
\email{tyler.hou.cs@gmail.com}
\extrainfo{\url{https://github.com/tylerhou}}

\nopagenumbers{}
\begin{document}
\makecvtitle

\section{Education}
\cventry{2013--2017}{Classical Diploma}{Phillips Exeter Academy}{Class of 2017}{cum laude}{}

\section{Skills}
\begin{multicols}{2}
\subsection{Fluent}
\cvline{languages}{TypeScript, JavaScript (ES6), Python, Ruby, C++}
\cvline{technologies}{Linux, React, Ruby on Rails, Git, PostgreSQL}
\columnbreak
\subsection{Have Experience}
\cvline{}{C, Java}
\cvline{}{Webpack, Node, \LaTeX}
\end{multicols}

\section{Work Experience}

\cventry{\small{10/2018-now}}{Software Engineer}{Google LLC}{Sunnyvale, CA}{}{}
\cventry{\small{9/2017--9/2018}}{Software Development Engineer}{Eden (YC S15)}{San Francisco, CA}{}{
\begin{itemize}
    \item Wrote libraries and tooling which used type hinting to empower developers to rapidly build fully-featured client side forms in React and seamless, type-safe GraphQL mutation endpoints for Rails. These tools reduced boilerplate by 80\% and saved hours of developer time per form or mutation.
    \item Designed a financial system to accurately track transactions, transaction amendments, invoices, and payments between partners and customers on Eden's marketplace platform, saving our finance and success teams 50+ hours per week.
    \item Designed the front-end architecture for a chat application for Eden's partners, customers, and account managers (after seven months, it has had less than three bugs in production).
\end{itemize}
}
\cventry{\small{2014--2017}}{Freelance Software Engineer}{Phillips Exeter Academy}{Exeter, NH}{}{
\begin{itemize}
\item Designed a new website for the Exeter Math Club with React, webapp2, and Google App Engine.\newline \url{https://exeter-math.appspot.com/}
\item Integrated with an online credit card payment provider for the Exonian Online newspaper.
\item Managed DNS and hosting for the website of Matter Magazine, an Exeter science publication.
\item Created a visualization of the k-means algorithm for teaching students at Exeter Computing Club. \newline \url{https://github.com/tylerhou/kmeans}
\end{itemize}
}

\section{Relevant Coursework}
\subsection{Phillips Exeter Academy}
\cvline{computer science}{\small\textbf{CSC420: Data Structures and Algorithms} (grade: A) \newline
\textbf{CSC999: Databases and Independent Study} (grade: A)}
\cvline{mathematics}{\small\textbf{Calculus I, II} (grade average: A),
\textbf{Linear Algebra} (grade: A), \textbf{Real Analysis} (grade: A-), \textbf{Topology} (A-)}
\subsection{Online Courseware}
\cvline{computer science}{\small Coursera: Andrew Ng's Stanford University \textbf{Machine Learning} (100\% completed) \newline \url{https://www.coursera.org/account/accomplishments/certificate/7XHNAP2HGLTL}}

\section{Projects}

\cventry{\small{2015}}{Connect Four}{}{}{\url{https://github.com/tylerhou/connectfour}}{
A connect four game GUI and AI for the CSC420 course in Java, built with negamax (a variant of minimax) plus alpha-beta pruning and a responsive, threaded UI.
}
\cventry{\small{2015}}{Flow}{}{}{\url{https://github.com/tylerhou/flow}}{
A physics simulation of circles undergoing perfectly elastic collisions in CoffeeScript.
}

\section{Other}
\cvline{interests}{fluent in Classical Latin and basic Ancient Greek; not-yet published poet and translator of questionable skill; a cappella and choir singer; Classical arch\ae ologist (\href{http://lykaionexcavation.org/}{Mt. Lykaion}).}

\newpage
\end{document}